---
title: "Task 3"
output:
  html_document:
#    code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=120)
#install.packages("car")
library(car)
#install.packages("ggplot2")
library(ggplot2)
#install.packages("reshape2")
library(reshape2)
```

####  Import the dataset Apartments.xlsx
```{r}

```
Description:

- Age: Age of an apartment in years
- Distance: The distance from city center in km
- Price: Price per m2
- Parking: 0-No, 1-Yes
- Balcony: 0-No, 1-Yes


#### Change categorical variables into factors
```{r}

```


#### Test the hypothesis H0: Mu_Price = 1900 eur. What can you conclude?
```{r}

```


#### Estimate the simple regression function: Price = f(Age). Save results in object fit1 and explain the estimate of regression coefficient, coefficient of correlation and coefficient of determination.
```{r}

```



#### Show the scateerplot matrix between Price, Age and Distance. Based on the matrix determine if there is potential problem with multicolinearity.
```{r}

```




#### Estimate the multiple regression function: Price = f(Age, Distance). Save it in object named fit2.
```{r}

```


#### Chech the multicolinearity with VIF statistics. Explain the findings.
```{r}

```



#### Calculate standardized residuals and Cooks Distances for model fit2. Remove any potentially problematic case (outlier or unit with big influence).
```{r}

```


#### Check for potential heteroskedasticity with scatterplot between standarized residuals and standrdized fitted values. Explain the findings.
```{r}

```

#### Are standardized residuals ditributed normally? Show the graph and formally test it. Explain the findings.
```{r}

```



#### Estimate the fit2 again without potentially excluded cases and show the summary of the model. Explain all coefficients.
```{r}

```




#### Estimate the linear regression function Price = f(Age, Distance, Parking and Balcony). Be careful to correctly include categorical variables. Save the object named fit3. 
```{r}

```



#### With function anova check if model fit3 fits data better than model fit2.
```{r}

```




#### Show the results of fit3 and explain regression coefficient for both categorical variables. Can you write down the hypothesis which is being tested with F-statistics, shown at the bottom of the output?
```{r}

```


#### Save fitted values and claculate the residual for apartment ID2.
```{r}

```



